Incentivizing Exploration with Unbiased History

### 2018-10-08 2level.tex
update some figures

%!TEX root = main.tex
\section{Warm-up: Two-level Recommendation Policy}
In this section, we are going to show a two-level recommendation policy that gets sublinear regret.
In this first level, we run $T_1$ \ALGG ``in parallel''. More specifically, we divide the first $T_1 \cdot \GdT$ agents into $T_1$ groups and agents only observe the history of all previous agents in the same group.
In the second level, we show the rest $T-T_1\cdot \GdT$ agents the history of first $T_1 \cdot \GdT$ rounds. We will pick $T_1$ in Theorem \ref{thm:2level}. 
See also Figure \ref{fig:2level} for a graphical view of the information flow.

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \filldraw[fill=blue!20!white]
 (0,2)--(10,2)--(10,3)--(0,3)--cycle;
  \filldraw[fill=red!20!white]
  (0,0)--(1,0)--(1,1)--(0,1)--cycle;
  \draw[dashed] (0.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (1,0)--(2,0)--(2,1)--(1,1)--cycle;
  \draw[dashed] (1.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (2,0)--(3,0)--(3,1)--(2,1)--cycle;
  \draw[dashed] (2.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (3,0)--(4,0)--(4,1)--(3,1)--cycle;
  \draw[dashed] (3.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (9,0)--(10,0)--(10,1)--(9,1)--cycle;
  \draw[dashed] (9.5,1)--(5,2);
  \node at(5,0.5){$\cdots$};
  \node at(6,0.5){$\cdots$};
  \node at(7,0.5){$\cdots$};
  \node at(8,0.5){$\cdots$};
  \node at(5,2.5){$T -T_1 \cdot \GdT$};
  \node at(0.5,0.5){$\GdT$};
  \node at(1.5,0.5){$\GdT$};
  \node at(2.5,0.5){$\GdT$};
  \node at(3.5,0.5){$\GdT$};
  \node at(9.5,0.5){$\GdT$};
  \node at(-2,0.5){\textbf{First Level}};
  \node at(-2,2.5){\textbf{Second Level}};
\end{tikzpicture}
\caption{2-level Recommendation Policy.}
\label{fig:2level}
\end{figure}

\begin{theorem}
\label{thm:2level}
With proper setting of $T_1$, our two-level recommendation policy gets expected regret $O(T^{2/3} \log(T)^{1/3})$. If we know the gap between the means of the best arm and second best arm is larger than $\Delta$, we can make the expected regret is $O(\log(T) \cdot \Delta^{-2})$. 
\end{theorem}

\begin{proof}
We will set $T_1$ later in the proof. For now, we just need to make $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$.

The first $T_1 \cdot \GdT$ rounds will get total regret at most $T_1 \cdot \GdT$.  We focus on the regret of the rest $T - T_1 \cdot \GdT$ rounds. We first consider the following two clean events and we show that they together imply upper bounds on $|\hat{\mu}^t_a - \mu_a|$'s for $t > T_1 \cdot \GdT$.

\begin{itemize}
\item For each arm $a$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level. By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$ Define $W_1^a$ to be the event that the number of arm $a$ pulls in the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)} \geq q_a T_1 / 2$. By Chernoff bound,
\[
\Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\item For each arm $a$, imagine there is a tape of $T$ arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agent pull arm $a$. Define $W^{a,t}_2$ to be the event that the empirical mean of the first $t$ pulls of arm $a$ is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$ to be the intersection of these events (i.e. $\bigcap_{a,t} W^{a,t}_2$).
By Chernoff bound,
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound, 
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]
\end{itemize}

@@

For any arm $a$ and agent $t$ in the second level, by $W_1$ and $W_2$, we have
\[
|\bar{\mu}^t_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}.
\]
By $W_1$ and Assumption \ref{ass:embehave}, we have
\[
|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{c_m}{\sqrt{q_aT_1/2}}.
\]
Therefore,
\[
|\bar{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}+\frac{c_m}{\sqrt{q_aT_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}
\]
So the second-level agents will pick an arm $a$ which has $\mu_a$ at most $6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$ away from $\mu_1$. To sum up, the total expected regret is at most 
\[
T_1 \cdot \GdT + T \cdot (1-\Pr[W_1 \cap W_2]) + T \cdot  6 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get expected regret $O(T^{2/3}\log(T)^{1/3})$.

>>>>

%!TEX root = main.tex
\section{Warm-up: 2-level Recommendation Policy}
In this section, we are going to show a 2-level recommendation policy that gets sublinear regret.

The 2-level recommendation policy is constructed as following.
In the first level, we run $T_1$ \ALGG of $\GdT$ rounds ``in parallel''. More specifically, we divide the first $T_1 \cdot \GdT$ agents into $T_1$ groups of equal size and agents only observe the history of all previous agents in the same group.
In the second level, we show the rest $T-T_1\cdot \GdT$ agents the history of first $T_1 \cdot \GdT$ rounds. We will pick $T_1$ in Theorem \ref{thm:2level}. 
See also Figure \ref{fig:2level} for a graphical view of the information flow.

The idea of this 2-level recommendation policy is simple. We first try to explore all arms enough amount of times in the first level using multiple runs of \ALGG under the guarantee of Lemma \ref{lem:greedy}. After that, by concentration argument, we can show that while observing the history of the first level, agents in the second level pick an arm with mean close to the best arm's mean.

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \filldraw[fill=blue!20!white]
 (0,2)--(10,2)--(10,3)--(0,3)--cycle;
  \filldraw[fill=red!20!white]
  (0,0)--(1,0)--(1,1)--(0,1)--cycle;
  \draw[dashed] (0.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (1,0)--(2,0)--(2,1)--(1,1)--cycle;
  \draw[dashed] (1.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (2,0)--(3,0)--(3,1)--(2,1)--cycle;
  \draw[dashed] (2.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (3,0)--(4,0)--(4,1)--(3,1)--cycle;
  \draw[dashed] (3.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (9,0)--(10,0)--(10,1)--(9,1)--cycle;
  \draw[dashed] (9.5,1)--(5,2);
  \node at(5,0.5){$\cdots$};
  \node at(6,0.5){$\cdots$};
  \node at(7,0.5){$\cdots$};
  \node at(8,0.5){$\cdots$};
  \node at(5,2.5){$T -T_1 \cdot \GdT$};
  \node at(0.5,0.5){$\GdT$};
  \node at(1.5,0.5){$\GdT$};
  \node at(2.5,0.5){$\GdT$};
  \node at(3.5,0.5){$\GdT$};
  \node at(9.5,0.5){$\GdT$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \draw[->] (11,0)--(11,3);
  \node at(11.5,1.5)[ rotate=90]{Time};
\end{tikzpicture}
\caption{2-level Recommendation Policy.}
\label{fig:2level}
\end{figure}

\begin{theorem}
\label{thm:2level}
With proper setting of $T_1$, the 2-level recommendation policy gets expected regret $O(T^{2/3} \log(T)^{1/3})$. If we know the gap between the means of the best arm and second best arm is larger than $\Delta$, we can make the expected regret $O(\log(T) \cdot \Delta^{-2})$. 
\end{theorem}

\begin{proof}
We will set $T_1$ later in the proof. For now, we just need to know we will make $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$. Since this recommendation policy is symmetric over arms, we wlog assume that arm 1 has the highest mean in the proof.

The first $T_1 \cdot \GdT$ rounds will get total regret at most $T_1 \cdot \GdT$.  We focus on bounding the regret of the rest $T - T_1 \cdot \GdT$ rounds. We consider the following two clean events. We will first bound the probability that both of them happen and then we will show that they together imply upper bounds on $|\hat{\mu}^t_a - \mu_a|$'s for any agent $t$ in the second level. Recall $\hat{\mu}^t_a$ is the estimated mean of arm $a$ by agent $t$ and agent $t$ picks the arm with the highest $\hat{\mu}^t_a$.

\begin{itemize}
\item For each arm $a$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level. By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. Define $W_1^a$ to be the event that the number of arm $a$ pulls in the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)} \geq q_a T_1 / 2$. By Chernoff bound,
\[
\Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\item For each arm $a$, imagine there is a tape of $T$ arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agent pull arm $a$. Define $W^{a,t}_2$ to be the event that the empirical mean of the first $t$ pulls of arm $a$ is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$ to be the intersection of these events (i.e. $\bigcap_{a,t} W^{a,t}_2$).
By Chernoff bound,
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound, 
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]
\end{itemize}

@@

For any arm $a$ and agent $t$ in the second level, by $W_1$ and $W_2$, we have
\[
|\bar{\mu}^t_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}.
\]
By $W_1$ and Assumption \ref{ass:embehave}, we have
\[
|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{c_m}{\sqrt{q_aT_1/2}}.
\]
Therefore,
\[
|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}+\frac{c_m}{\sqrt{q_aT_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
So the second-level agents will pick an arm $a$ which has $\mu_a$ at most $6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$ away from $\mu_1$. To sum up, the total expected regret is at most 
\[
T_1 \cdot \GdT + T \cdot (1-\Pr[W_1 \cap W_2]) + T \cdot  6 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get expected regret $O(T^{2/3}\log(T)^{1/3})$.

### 2018-10-08 3level.tex
A figure for 3-level
update some figures

\section{Three-level Recommendation Policy}
In this section, we show how to get $o(T^{2/3})$ regret with a 3-level recommendation policy. For simplicity, we assume there are only 2 arms.

For 3-level recommendation policy, set $T_1 = T^{4/7}\log^{-1/7}(T)$ and $T_2 = T^{6/7}\log^{-5/7}(T)$. The first level has $S = 2^{10}\log(T)$ groups of agents. Each group runs $T_1$ \ALGG of $T_G$ rounds in parallel. The second level also has $S$ groups of agents. Each group has $T_2$ agents and they observe the history of corresponding group in the first level. All the rest agents are in the third level and they observe the entire history of the first two levels.

Needs to draw a figure here.

@@

\begin{proof}
Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. We do a case analysis based on $\mu_1-\mu_2$. (some intuition and explanation of these cases?)

@@

\item For all the groups in the first two levels and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in the first two levels pull arm $a$. Define $W_3^{a,t}$ to be the event that the mean of the first $t$ pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$.

By Chernoff bound, 
\[
\Pr[W_3^{a,t}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
\]
Define $W_3$ to be the intersection of all these events (i.e. $W_3 = \bigcap_{a,t} W_3^{a,t}$). By union bound, we have
\[
\Pr[W_3] \geq 1- \frac{4}{T^3}.
\]

\item Consider the tapes defined in the second bullet again. For the $s$-th first-level group and arm $a$, define $W_4^{s,a,high}$  to be the event that first $q_a T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at least $\mu_a + 1/\sqrt{q_a T_1}$ and define  $W_4^{s,a,low}$  to be the event that first $q_a T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at most $\mu_a - 1/\sqrt{q_a T_1}$. By Berry-Essen Theorem and $\mu_a \in [1/3,2/3]$, we have
\[
\Pr[W_4^{s,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{q_aT_1}} > 1/4.
\]
The last inequality follows when $T$ is larger than some constant.
Similarly we also have 
\[
\Pr[W_4^{s,a,low}] > 1/4.
\]
Since $W_4^{s,a,high}$ is independent with $W_4^{s,3-a,low}$, we have
\[
\Pr[W_4^{s,a,high} \cap W_4^{s,3-a,low}] =\Pr[W_4^{s,a,high}] \cdot  \Pr[W_4^{s,3-a,low}]>(1/4)^2 = 1/16.
\]
Now define $W_4$ as $\bigcap_a \bigcup_s (W_4^{s,a,high} \cap W_4^{s,3-a,low})$. Notice that $(W_4^{s,a,high} \cap W_4^{s,3-a,low})$ are independent across different $s$'s. So by union bound, we have
\[
\Pr[W_4] \geq 1- 2(1-1/16)^S \geq 1 -2 /T.
\]
\end{itemize}

By union bound, the intersection of these clean events (i.e. $\bigcap_{i=1}^4 W_i$) happens with probability $1-O(1/T)$. When this intersection does not happen, since the probability is $O(1/T)$, it cost expected regret $O(1/T) \cdot T = O(1)$.

>>>>

\section{3-level Recommendation Policy}
In this section, we show how to get $o(T^{2/3})$ regret with a 3-level recommendation policy. For simplicity, we assume there are only 2 arms.

The 3-level recommendation policy is constructed as followings. Set $T_1 = T^{4/7}\log^{-1/7}(T)$ and $T_2 = T^{6/7}\log^{-5/7}(T)$. The first level has $S = 2^{10}\log(T)$ groups of agents. Each group runs $T_1$ \ALGG of $T_G$ rounds in parallel. The second level also has $S$ groups of agents. Each group has $T_2$ agents and they observe the history of corresponding group in the first level. All the rest agents are in the third level and they observe the entire history of the first two levels. 
See also Figure \ref{fig:3level} for a graphical view of the information flow.

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \filldraw[fill=green!20!white]
 (0,4)--(10,4)--(10,5)--(0,5)--cycle;
 \foreach \x in {0,3,8}
 {
 \filldraw[fill=blue!20!white]
 (\x+0,2)--(\x+2,2)--(\x+2,3)--(\x+0,3)--cycle;
 \draw[dashed] (\x+1,3)--(5,4);
 \filldraw[fill=red!20!white]
 (\x+0,0)--(\x+2,0)--(\x+2,1)--(\x+0,1)--cycle;
 \draw[dashed] (\x+1,1)--(\x+1,2);
 \draw[dashed] (\x+0.2,1)--(\x+1,2);
 \draw[dashed] (\x+0.6,1)--(\x+1,2);
 \draw[dashed] (\x+1.4,1)--(\x+1,2);
 \draw[dashed] (\x+1.8,1)--(\x+1,2);
 \draw[dashed] (\x+0.4,0)--(\x+0.4,1); 
 \draw[dashed] (\x+0.8,0)--(\x+0.8,1); 
 \draw[dashed] (\x+1.2,0)--(\x+1.2,1); 
 \draw[dashed] (\x+1.6,0)--(\x+1.6,1);  
 \node at(\x+1,2.5){$T_2$};
 \node at(\x+1,0.5){$T_1 \cdot \GdT$};
 }
  \node at(5,4.5){$T -S(T_1 \cdot \GdT + T_2)$};
  \node at (6,1.5){$\cdots$};
  \node at (7,1.5){$\cdots$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \node at(-1,4.5){\textbf{Levle 3}};
  \draw[->] (11,0)--(11,5);
  \node at(11.5,2.5)[ rotate=90]{Time};
\end{tikzpicture}
\caption{3-level Recommendation Policy.}
\label{fig:3level}
\end{figure}

@@

\begin{proof}
Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. We do a case analysis based on $\mu_1-\mu_2$.

@@

\item For all the groups in the first two levels and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in the first two levels pull arm $a$. Define $W_3^{a,t}$ to be the event that the mean of the first $t$ pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. By Chernoff bound, 
\[
\Pr[W_3^{a,t}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
\]
Define $W_3$ to be the intersection of all these events (i.e. $W_3 = \bigcap_{a,t} W_3^{a,t}$). By union bound, we have
\[
\Pr[W_3] \geq 1- \frac{4}{T^3}.
\]

\item Consider the tapes defined in the second bullet again. For the $s$-th first-level group and arm $a$, define $W_4^{s,a,high}$  to be the event that first $q_a T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at least $\mu_a + 1/\sqrt{q_a T_1}$ and define  $W_4^{s,a,low}$  to be the event that first $q_a T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at most $\mu_a - 1/\sqrt{q_a T_1}$. By Berry-Essen Theorem and $\mu_a \in [1/3,2/3]$, we have
\[
\Pr[W_4^{s,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{q_aT_1}} > 1/4.
\]
The last inequality follows when $T$ is larger than some constant.
Similarly we also have 
\[
\Pr[W_4^{s,a,low}] > 1/4.
\]
Since $W_4^{s,a,high}$ is independent with $W_4^{s,3-a,low}$, we have
\[
\Pr[W_4^{s,a,high} \cap W_4^{s,3-a,low}] =\Pr[W_4^{s,a,high}] \cdot  \Pr[W_4^{s,3-a,low}]>(1/4)^2 = 1/16.
\]
Now define $W_4$ as $\bigcap_a \bigcup_s (W_4^{s,a,high} \cap W_4^{s,3-a,low})$. Notice that $(W_4^{s,a,high} \cap W_4^{s,3-a,low})$ are independent across different $s$'s. By union bound, we have
\[
\Pr[W_4] \geq 1- 2(1-1/16)^S \geq 1 -2 /T.
\]
\end{itemize}

By union bound, the intersection of these clean events (i.e. $\bigcap_{i=1}^4 W_i$) happens with probability $1-O(1/T)$. When this intersection does not happen, since the probability is $O(1/T)$, it contributes $O(1/T) \cdot T = O(1)$ to the expected regret.

### 2018-10-08 llevel.tex
update some figures

>>>>

\begin{corollary}
With the proper setting of $L$ and $T_1,...,T_L$ discribed above, the $L$-level recommendation policy gets expected regret $O(polylog(T) /\Delta)$. Here $\Delta = \mu_1 -\mu_2$ and the $L$-level recommendation policy does not need to know $\Delta$ ahead of the time. Moreover, agent $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$. 
\end{corollary}

\begin{proof}
\end{proof}
